\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}

This thesis was written under the framework of the ALGANT DOC program supported
by the European Union, and I was very lucky to spend my PhD between Bordeaux and
Leiden, both being places of great importance in number theory.

Above all, I am deeply grateful to my advisors, \personality{Baptiste Morin} and
\personality{Bas Edixhoven}, who have taught me a lot of mathematics and showed
exceptional kindness and patience. Their support means a lot to me, both
mathematically and personally.

I thank \personality{Stephen Lichtenbaum} and
\personality{Niranjan Ramachandran} for being the referees and providing their
invaluable feedback.

It is also important to mention the influence of \personality{Matthias Flach}:
I have learned many ideas that appear here from reading his joint paper with
Baptiste Morin.

I would also like to thank \personality{Yuri Bilu} for his support, his
dedication to the ALGANT program over the years, and above all his influence on
my number theoretical education.

\personality{Boas Erez} introduced me to arithmetic geometry during my master
studies in Bordeaux and also introduced me to Baptiste Morin.

I am also indebted to \personality{Nikola\u{\i} Mishachev} and
\personality{Dmitri\u{\i} Pasechnik} for their support during my early steps in
mathematics.

On the personal side, I am grateful to \personality{Gabriel Chicas Reyes} for
all the experiences shared together, to my brother
\personality{Dmitri\u{\i} Beshenov}, and to all of my friends and fellow PhD
students from Milan, Bordeaux, and Leiden, particularly
\personality{Javier Estrada}, \personality{Andrea Gagna},
\personality{Mauro Mantegazza}, \personality{Chloe Martindale},
\personality{Maxim Mornev}, \personality{Frances Odumodu},
\personality{Giulio Orecchia}, \personality{Dima Shvetsov},
\personality{Pavel Solomatin}, \personality{José Villanueva}, and
\personality{Rosa Winter}.

\pagebreak

\begin{otherlanguage}{spanish}
  Agradezco a toda la familia \personality{López Aravena} y particularmente a
  \mbox{\personality{Olga}}, \personality{Angélica ``Kika''},
  \personality{Héctor ``Tito''}, \personality{Cristian} y \personality{Paolo}
  por su compañía durante mi estancia en Burdeos, todas las experiencias
  compartidas y por hacer más feliz mi vida de estudiante en Francia.

  Y por último, pero no menos importante, les doy gracias a mis amigos
  salvadoreños: \personality{Mario Carpio}, \personality{Jorge Flores},
  \personality{Diana Herrera} y \personality{Yoceman Sifontes}, y también al
  Ministro \personality{Carlos Canjura}, \personality{Nerys Funes} y
  \personality{Américo Hidalgo} por su apoyo en San Salvador donde terminé de
  redactar esta tesis.
\end{otherlanguage}
